Modal Abstractions for Virtualizing Memory Addresses

### 2025-08-22 relwork.tex
fix relwork re: syeda and klein

The only \replace{other attempt to verify a change of address space was by}{work to tackle TLB code verification was}
\citet{syeda2018program,syeda2020formal},
\replace{whose focus was on TLB maintenance (which we do not model)}{who are also the only prior work on verifying address-space-aware context switching}.
However, they verified only the 4 instructions to switch address spaces and update the TLB on an ARM processor, in isolation
(i.e., not the full context switch including changing stacks with address spaces).
The specification they proved for those instructions did not address program invariants that may be valid in one address space and not the other,
so is not flexible enough to extend directly to a full context switching primitive as in Figure \ref{fig:swtchC}\replace{,}{.}
\add{Their logic adds an assertion tracking known-inconsistent addresses (i.e., recently-unmapped by a table update or change in page table root)
and their memory access rules require accessed memory to lie outside that set.
However their logic is proven sound against a generalized semantics where any page table change adds \emph{all}
addresses to the inconsistent set, which is too imprecise for finer-grained unmapping.
}
The right \replace{eventual}{general} solution would be to combine our work
and \add{an extension of} theirs, \add{a substantial project} which we leave to future work\replace{,}{.}
\add{
 No other prior work has considered address space changes during context switching. \textsc{XCAP}~\cite{ni2007contexts}
 and Bedrock~\cite{Chlipala2011Bedrock,Chlipala2013Bedrock,Chlipala2015webapp} deal
 only with usermode threading (in a single process). \textsc{CertiKOS} and \textsc{seL4} trust assembly primitives for
 context switches, and do  not model address translation for executing code.
 \looseness=-1
}

>>>>

The only \replace{other attempt to verify a change of address space was by}{work to tackle TLB code verification was}
\citet{syeda2018program,syeda2020formal},
\replace{whose focus was on TLB maintenance (which we do not model)}{who are also the only prior work on verifying address-space-aware context switching}.
However, they verified only the 4 instructions to switch address spaces and update the TLB on an ARM processor, in isolation
(i.e., not the full context switch including changing stacks with address spaces).
The specification they proved for those instructions did not address program invariants that may be valid in one address space and not the other,
so is not flexible enough to extend directly to a full context switching primitive as in Figure \ref{fig:swtchC}\replace{,}{.}
\add{Their logic adds an assertion tracking known-inconsistent addresses (i.e., recently-unmapped by a table update or change in page table root)
and their memory access rules require accessed memory to lie outside that set.
% However their logic is proven sound against a generalized semantics where
% any page table change adds \emph{all}
% addresses to the inconsistent set,
% which is too imprecise for finer-grained unmapping.
However in their logic,
reasoning about updates to the inconsistent set (from a page table update)
requires direct reasoning
directly about the physical memory heap, which limits modularity.
}
The right \replace{eventual}{general} solution would be to combine our work
and \add{an extension of} theirs, \add{a substantial project} which we leave to future work\replace{,}{.}
\add{
 No other prior work has considered address space changes during context switching. \textsc{XCAP}~\cite{ni2007contexts}
 and Bedrock~\cite{Chlipala2011Bedrock,Chlipala2013Bedrock,Chlipala2015webapp} deal
 only with usermode threading (in a single process). \textsc{CertiKOS} and \textsc{seL4} trust assembly primitives for
 context switches, and do  not model address translation for executing code.
 \looseness=-1
}
